---
title: "In-Class Exercises"
sidebar: false
engine: knitr
filters:
  - webr
webr:
  cell-options:
    editor-font-scale: 0.85
    fig-width: 6
    fig-height: 3.7
    out-width: "70%"
---

::: {.callout-note}
## Attribution Note

These exercises have been shamelessly copied from the R-Primers project created
by [Andrew Heiss](https://www.andrewheiss.com/). The original version of Heiss'
website is available [here](https://r-primers.andrewheiss.com/index.html).
:::

```{r include = FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6 * 0.618,
  fig.retina = 3,
  dev = "ragg_png",
  fig.align = "center",
  out.width = "70%"
)

source(here::here("R", "helpers.R"))
```

The in-class portion of this week's practical exercises will extend the introduction
that you recieved in the At-Home Exercises by digging deeper into techniques for
transforming, visualizing, and tidying data.

##

```{r}
#| echo: false
#| results: asis
begin_buttons("transform-data/01-tibbles/index.html")
```
