---
title: "At-Home Exercises"
sidebar: false

engine: knitr
filters:
  - webr
webr:
  cell-options:
    editor-font-scale: 0.85
    fig-width: 6
    fig-height: 3.7
    out-width: "70%"
---

::: {.callout-note}
## Attribution Note

This project is a blatant clone of the R-Primers project created by
[Andrew Heiss](https://www.andrewheiss.com/). The original version of this website
is available [here](https://r-primers.andrewheiss.com/index.html).

If you've somehow stumbled onto this page in the wild, you should probably use
Heiss' original version of this project. I'm only hosting my own copy of these
materials to ensure that the content of the tutorials doesn't change in the middle
of a course in which I'm relying on this resource.

The remainder of this page comprises Heiss' original content.
:::

```{r include = FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6 * 0.618,
  fig.retina = 3,
  dev = "ragg_png",
  fig.align = "center",
  out.width = "70%"
)

source(here::here("R", "helpers.R"))
```

The at-home portion of this week's practical exercises will introduce you to the
rudements of data visualization and statistical programming in R.

##

```{r}
#| echo: false
#| results: asis
create_buttons("basics/01-visualization-basics/index.html")
```
